Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-11-27 inst/paper/main.tex
mijor

\subsection{Eval Semantics}
Originally, \eval was limited to interpreted languages, but with the
advent of just-in-time compilation this restriction was gradually
lifted.

@@

\medskip\emph{Discussion:~} There are two outstanding differences that set
the design of \eval in R apart from JavaScript. On the usability side, \eval
does not take a string, but an AST and an environment. This is slightly more
involved than just taking a string and may discourage some casual users.
The second substantial difference is the control that R gives over the
choice of environment in which the AST is evaluated in. Beside traditional
choices such as the top level or current lexical environment, R allows
programmers to choose a fresh, empty, environment or any environment on the
call stack. This is a significant increase in expressive power as functions
that are otherwise not aware of the use of \eval may be deeply impacted.

>>>>

\subsection{Eval Semantics}

There are two outstanding differences that set
the design of \eval in R apart from JavaScript. On the usability side, \eval
does not take a string, but an AST and an environment. This is slightly more
involved than just taking a string and may discourage some casual users.
The second substantial difference is the control that R gives over the
choice of environment in which the AST is evaluated in. Beside traditional
choices such as the top level or current lexical environment, R allows
programmers to choose a fresh, empty, environment or any environment on the
call stack. This is a significant increase in expressive power as functions
that are otherwise not aware of the use of \eval may be deeply impacted.

Originally, \eval was limited to interpreted languages, but with the
advent of just-in-time compilation this restriction was gradually
lifted.

@@
